Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-30 paper/aldebaran.tex
Pope, Davies swap in author order.
Only w.farr@bham.ac.uk on email.
wording

@@

\email{w.farr@bham.ac.uk, G.R.Davies@bham.ac.uk, benjamin.pope@nyu.edu, txn016@student.bham.ac.uk, jimbarrett27@gmail.com}

@@

For several reasons we are not convinced that this poses an issue for Aldebaran or for K~giant RV planets more generally. \citet{2018arXiv180105239H} suggest that the new type of stellar variability may be oscillatory convective modes, but both Aldebaran and Eltanin have much lower luminosities and longer periods than would seem to be allowed by the period-luminosity relation for these otherwise unobserved modes \citep[Figure~9]{2015MNRAS.452.3863S,2018arXiv180105239H}. If these are identified with the long secondary periods (LSPs) observed in some bright red giants ($L \approx 1000 \lsun$), then Aldebaran and Eltanin are both too faint, and lack the mid-IR excess typical of LSP stars \citep{2009ApJ...707..573W}. It would also be surprising if the shape of the RV curve could reproduce the harmonic structure of an eccentric Keplerian such as in Aldebaran~b ($e = \EccentricityRange{}$), let alone the much higher eccentricities observed in other giants \citep[e.g. $\iota$~Dra~b, $e=0.7$:][]{2002ApJ...576..478F}.

It would be a cruel conspiracy of nature if red giants support a type of oscillation which is common and closely resembles a planetary signal. We believe this cannot be the case: the populations of planets around subgiants and giants evolved from intermediate mass stars are similar \citep{2014A&A...566A.113J}, as expected if subgiants evolve into giants and retain their planetary systems in a similar configuration, and with very different stellar structures subgiants and giants are unlikely to share similar modes of long-period pulsation. The similarity of distributions of systems hosted by subgiant and giants could not be reproduced if a large fraction of the giants' planets were false positives. Moreover giant planets are expected to be common around intermediate-mass stars \citep{2008ApJ...673..502K}, and some are definitely known to be bona fide planets because they transit their star \citep[e.g.][]{2014A&A...562A.109L,2015A&A...573L...6O,2016AJ....152..185G,2017AJ....154..254G}.

>>>>

\email{w.farr@bham.ac.uk}

@@

@@

For several reasons we are not convinced that this poses an issue for Aldebaran or for K~giant RV planets more generally. \citet{2018arXiv180105239H} suggest that the new type of stellar variability may be oscillatory convective modes, but both Aldebaran and Eltanin have much lower luminosities and longer periods than would seem to be allowed by the period-luminosity relation for these otherwise unobserved modes \citep[Figure~9]{2015MNRAS.452.3863S,2018arXiv180105239H}. If these are identified with the long secondary periods (LSPs) observed in some bright red giants ($L \approx 1000\, \lsun$), then Aldebaran and Eltanin are both too faint, and lack the mid-IR excess typical of LSP stars \citep{2009ApJ...707..573W}. It would also be surprising if the shape of the RV curve could reproduce the harmonic structure of an eccentric Keplerian such as in Aldebaran~b ($e = \EccentricityRange{}$), let alone the much higher eccentricities observed in other giants \citep[e.g. $\iota$~Dra~b, $e=0.7$:][]{2002ApJ...576..478F}.

It would be a cruel conspiracy of nature if red giants support a type of oscillation which is common and closely resembles a planetary signal. We believe this cannot be the case: the populations of planets around subgiants and giants evolved from intermediate mass stars are similar \citep{2014A&A...566A.113J}, as expected if subgiants evolve into giants and retain their planetary systems, and with very different stellar structures subgiants and giants are unlikely to share modes of long-period pulsation. The similarity of distributions of systems hosted by subgiant and giants could not be reproduced if a large fraction of the giants' planets were false positives. Moreover giant planets are expected to be common around intermediate-mass stars \citep{2008ApJ...673..502K}, and some are definitely known to be bona fide planets because they transit their star \citep[e.g.][]{2014A&A...562A.109L,2015A&A...573L...6O,2016AJ....152..185G,2017AJ....154..254G}.
